### 2020-04-23 final_report/methodology.tex
blow up tables, finalise appendix A layout

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llrl}
		\toprule
		Regression performance metrics	& Mathematical formulation / description &
		\multicolumn{2}{c}{Ideal value [units]} \\
		\midrule
		Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
									& [TBR] \\
		Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
		\hat{y}^{(i)}| \right\} $	 & 0 & [TBR] \\
		Coefficient of determination $R^2$	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
		\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 & [rel.] \\
		Adjusted $R^2$	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 & [rel.] \\
		\midrule
		Evaluation time metrics	& {} & {} & {} \\
		\midrule
		Mean training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
		$\hat{f}(x)$})/N_0$ 	& 0 & [ms] \\
		Mean prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
		$\hat{f}(x)$})/N$	& 0 & [ms] \\
		Relative speedup	& $(\text{wall evaluation time of $f(x)$}) /
		(N\overline{t}_{\text{pred.}})$	&
		$\to\infty$ & [rel.] \\
		\bottomrule
		\end{tabular}
	}
	\caption{Metrics recorded in supervised learning experiments. In
	formulations, we work with training set of size $N_0$ and testing set of
size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in the expensive model and the surrogate
respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
number of input features.}
	\label{tbl:metrics}
\end{table}

>>>>

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llrl}
		\toprule
		Regression performance metrics	& Mathematical formulation / description &
		\multicolumn{2}{c}{Ideal value [units]} \\
		\midrule
		Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
									& [TBR] \\
		Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
		\hat{y}^{(i)}| \right\} $	 & 0 & [TBR] \\
		Coefficient of determination $R^2$	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
		\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 & [rel.] \\
		Adjusted $R^2$	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 & [rel.] \\
		\midrule
		Evaluation time metrics	& {} & {} & {} \\
		\midrule
		Mean training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
		$\hat{f}(x)$})/N_0$ 	& 0 & [ms] \\
		Mean prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
		$\hat{f}(x)$})/N$	& 0 & [ms] \\
		Relative speedup $\sigma$	& $(\text{wall evaluation time of $f(x)$}) /
		(N\overline{t}_{\text{pred.}})$	&
		$\to\infty$ & [rel.] \\
		\bottomrule
		\end{tabular}
	}
	\caption{Metrics recorded in supervised learning experiments. In
	formulations, we work with training set of size $N_0$ and testing set of
size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in the expensive model and the surrogate
respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
number of input features.}
	\label{tbl:metrics}
\end{table}
